%% AMS-LaTeX Created with the Wolfram Language : www.wolfram.com

\documentclass{article}
\usepackage{amsmath, amssymb, graphics, setspace}

\newcommand{\mathsym}[1]{{}}
\newcommand{\unicode}[1]{{}}

\newcounter{mathematicapage}
\begin{document}

\title{Linear Algebra}
\author{}
\date{}
\maketitle

In a town with \(n\) people, \(m\) clubs have been formed. Every club have an odd number of members, and every two clubs have an even number of members
in common. Prove that \(m \leq  n\).

Let \(N=2^n\) for some positive integer \(n\) and \(\omega =e^{\frac{2\pi  i}{N}}\). { } Let \(U(\omega )\) be the \(N\times N\) matrix with \(U(\omega
)_{i,j}= \omega ^{(i-1)(j-1)}\). { } Compute { }\(U(\omega )U\left(\omega ^{-1}\right)\).

Let \(A\) and \(B\) be \(n\times n\) matrices satisfying \(A+B = A B\). Show that \(A B = B A\).

 Consider the matrix equation \(\left(
\begin{array}{ccc}
 1 & 1 & 0 \\
 1 & 1 & 1 \\
 0 & 1 & 1 \\
\end{array}
\right)^3=\left(
\begin{array}{ccc}
 A_n & B_n & C_n \\
 D_n & E_n & F_n \\
 G_n & H_n & J_n \\
\end{array}
\right)\). { } Identify \(A_n\), \(B_n\),$\ldots $, \(J_n\).

Let{'}s call a real 3 $\times $ 3 matrix a {``}magic square{''} if all its row-sums and column-sums are equal to 0. Show that all magic squares form
a vector space. Find its dimension.

Let \(n\) be a positive integer, and let \(v_1, v_2, \ldots ,v_k\), \(1\leq k\leq n\), be linearly independent vectors in \(\mathbb{R}^n\) spanning
a subspace \(V_k\). { }Prove that there exist \(k\) { }orthogonal vectors \(w_1, w_2, \ldots ,w_k\) that span \(V_k\). { } (Two vectors are orthogonal
if their dot product is equal to 0.) { }Hint: { }Use the linearly of the dot product: { }\(x.(a y+z) = a(x.y)+x.z\), where \(a\) is a scalar.

Let \(A\) be the \(n\times n\) matrix whose entry in the \(i\)-th row and \(j\)-th column is { }\(\frac{1}{\min (i,j)}\) { }for \(1 \leq  i,j \leq
 n\). Compute \(\det (A)\).

The dashboard of a nuclear power station has several lights. Some lights are on and some are off. There are also several buttons. Pressing each button
changes the state of several lights (from on to off and from off to on). It is known that for every set of lights there exists a button connected
to an odd number of lights in this set. Show that one can turn off all lights by pressing some buttons.

Compute the determinant of the \(n \times  n\) matrix \(\left[a_{i j}\right]\) such that \(a_{i j} =|i-j|\).

It is well known that all real-valued functions on \(\mathbb{R}\) form a vector space. Does the function \(\sin  x\) belong to the linear span of
the functions \(1\), \(\cos  x\), \(\cos  2 x\), \(\cos  3 x,\ldots\)? { } { } { } How about the function \(\sin ^2 x\)?

Think of a square matrix as placed on a checkerboard, so that the leading diagonal consists entirely of white squares. Then if the signs of all the
entries on black squares are changed, prove that the eigenvalues are unchanged.

\end{document}
