%% AMS-LaTeX Created with the Wolfram Language : www.wolfram.com

\documentclass{article}
\usepackage{amsmath, amssymb, graphics, setspace}

\newcommand{\mathsym}[1]{{}}
\newcommand{\unicode}[1]{{}}

\newcounter{mathematicapage}
\begin{document}

\title{Counting and Indirect Proofs}
\author{}
\date{}
\maketitle

Examples\\
A. Derive a formula for the number of \(k\) element subsets of an \(n\) element set , \(0\leq k\leq n\).\\
B. Prove that there is no least positive real number.

Let \textit{ S} be a set of real numbers which is closed under multiplication (that is, if \textit{ a} and \textit{ b} are in \textit{ S}, then so
is \(a b\)). Let \textit{ T} and \textit{ U} be disjoint subsets of \textit{ S} whose union is \textit{ S}. Given that the product of any three (not
necessarily distinct) elements of \textit{ T} is in \textit{ T} and that the product of any three elements of \textit{ U} is in \textit{ U}, show
that at least one of the two subsets \textit{ T}, \textit{ U} is closed under multiplication.

Let's say I have a group of \(n+1\) people who want to see a show. I have three tickets into the theatre: a backstage pass and two regular (but distinguishable)
tickets. I have to give out the tickets according to the following two rules:

The backstage pass must go to the oldest person who gets a ticket. (All the people in line are of different ages.

The person who gets the backstage pass can't get either of the other two tickets, but the two normal tickets can both go to the same person.

How many ways can I give away the tickets? { }There are two ways to count. Try to find both.

 Consider paths such as the one in the grid below that start at the bottom left, \((0,0),\) and reach the top right, \((10,10)\). { } These paths
can only go up and to the right. { } How many paths are there in all? { }How many of those paths pass through the point \((4,6)\)? { } Generalize
both of your results.

 { }\(\)

Prove that if \(n\geq 1\), then { }\(\binom{2 n}{n}=\sum _{k=0}^n \binom{n}{k}^2\)

Prove that the number of odd coefficients in each row of Pascal{'}s triangle is a power of 2.

Every point of three-dimensional space is colored red, green, or blue. Prove that one of the colors attains all distances, meaning that any positive
real number represents the distance between two points of this color.

There are 650 distinct points inside a disc of radius 16. Prove that there is an annulus with inner radius 2 and outer radius 3 on which lie at least
10 of the given points.

 How many positive integers \textit{ n} are there such that \textit{ n} is a divisor of at least one the numbers \(10^{40}\) and \(20^{30 }\)?

Prove that a list can be made of all the subsets of a finite set such that

 (i) the empty set is the first set;\\
(ii) each subset occurs once;\\
(iii) each subset is obtained from the preceding by adding or deleting an element.

\end{document}
